# setup
## load
```{r}
rm(list=ls())

knitr::opts_chunk$set(echo = FALSE)

library(lme4)
library(statmod)
library(DHARMa)
library(brms)
library(glmmTMB)

pathToFolder <- "/Users/dbao/My_Drive/road_construction/data/2022_online/"
save_folder <- file.path(pathToFolder, 'stat_model')

data_puzzle_level <- read.csv(file.path(pathToFolder, 'R_analysis_data/data.csv'))
data_choice_level <- read.csv(file.path(pathToFolder, 'R_analysis_data/choice_level/choicelevel_data.csv'))
```

## transform data
```{r}
data_choice_level$subjects <- factor(data_choice_level$subjects)
data_choice_level$firstUndo <- factor(data_choice_level$firstUndo)

data_puzzle_level$subjects <- factor(data_puzzle_level$subjects)
```

# more undos till the end
## number of cities within reach
```{r}
idx = (data_choice_level['condition']==1)&(data_choice_level['currNumCities']!=1)
data_subset = data_choice_level[idx, c("subjects", "within_reach","leftover", "currNumCities","allMAS","firstUndo")]
data_subset["step"] = data_subset$currNumCities / data_subset$allMAS
```

```{r}
# model_undo <- lme4::glmer(firstUndo ~  1 + log(1+within_reach) + (1|subjects),
#                   data = data_subset, family = binomial(link="cloglog"))
model_undo <- glm(firstUndo ~  1 + sqrt(within_reach),
                  data = data_subset, family = binomial)
summary(model_undo)
simulationOutput <- simulateResiduals(fittedModel = model_undo, plot = F)
```

```{r}
plot(simulationOutput)
```

```{r}
ita <- predict(model_undo)
working_resi <- resid(model_undo, type="working")
working_resp <- ita + working_resi
plot(working_resp, ita)
```
## remaining budget
```{r}
model_undo = glm(firstUndo ~  1 + sqrt(leftover),
                                  data = data_subset, family = "binomial")

# get the coefficients for the best fitting model
summary(model_undo)
simulationOutput <- simulateResiduals(fittedModel = model_undo, plot = F)
```
```{r}
plot(simulationOutput)
```
```{r}
ita <- predict(model_undo)
working_resi <- resid(model_undo, type="working")
working_resp <- ita + working_resi
plot(working_resp, ita)

```
## step
```{r}
model_undo = glm(firstUndo ~  1 + step ,
                                  data = data_subset, family = "binomial")

# get the coefficients for the best fitting model
summary(model_undo)
simulationOutput <- simulateResiduals(fittedModel = model_undo, plot = F)
```
```{r}
plot(simulationOutput)
```

## end state/ non-end
```{r}
idx = (data_choice_level['condition']==1)&(data_choice_level['currNumCities']!=1)
data_subset = data_choice_level[idx,]

end = (data_subset$checkEnd == 1)&(data_subset$submit != 1)
index_undo = as.numeric(rownames(data_subset[end,])) + 1
invalid = setdiff(index_undo, as.numeric(rownames(data_subset)))
index_undo_valid = setdiff(index_undo, invalid)
df_end_undo = data_choice_level[index_undo_valid, c('firstUndo','subjects','puzzleID')]

notend = (data_subset$checkEnd != 1)&(data_subset$submit != 1)
index_undo = as.numeric(rownames(data_subset[notend,])) + 1
invalid = setdiff(index_undo, as.numeric(rownames(data_subset)))
index_undo_valid = setdiff(index_undo, invalid)
df_notend_undo = data_choice_level[index_undo_valid, c('firstUndo','subjects','puzzleID')]

df_end_undo["type"] = "terminal"
df_notend_undo["type"] = "non-terminal"
undo_end_df = rbind(df_end_undo, df_notend_undo)
```

```{r}
model_undo_end = glm(firstUndo ~  1 + type,
                                  data = undo_end_df, family = "binomial")

# get the coefficients for the best fitting model
summary(model_undo_end)
simulationOutput <- simulateResiduals(fittedModel = model_undo_end, plot = F)
```
```{r}
plot(simulationOutput)
testOutliers(simulationOutput)
outliers(simulationOutput)
```

# dissatisfaction with the number of connected cities at the end, when there are no 
## current number of connected citie at the end
```{r}
# undo ----
index_first_undo =  as.numeric(rownames(data_choice_level[data_choice_level['undo'] == 1,])) # undo, not necessarily the first undo 
df_beforeUndo = data_choice_level[index_first_undo-1,] # index before that
df_beforeUndo = df_beforeUndo[df_beforeUndo$currMas == df_beforeUndo$allMAS,] # there are no errors
index_end_undo = as.numeric(rownames(df_beforeUndo[df_beforeUndo['checkEnd'] == 1,])) # end of trial
currNumCities_undo = data_choice_level[index_end_undo,c('currNumCities','subjects','puzzleID','leftover')] # remaining budget

# submit ----
index_notundo = as.numeric(rownames(data_choice_level[(data_choice_level['submit'] == 1)&(data_choice_level['condition'] == 1),])) # submit
df_notbeforeUndo = data_choice_level[index_notundo-1,]
df_notbeforeUndo = df_notbeforeUndo[df_notbeforeUndo$currMas == df_notbeforeUndo$allMAS,]
index_end_notundo = as.numeric(rownames(df_notbeforeUndo[(df_notbeforeUndo['checkEnd'] == 1),]))
currNumCities_notundo = data_choice_level[index_end_notundo,c('currNumCities','subjects','puzzleID','leftover')]

currNumCities_undo['submit'] = 0
currNumCities_notundo['submit'] = 1
currNumCities_df = rbind(currNumCities_undo, currNumCities_notundo)

```

```{r}

model_submit1 = lme4::glmer(submit ~  1 + currNumCities + (1 |subjects),
                                  data = currNumCities_df, family = "binomial")
summary(model_submit1)
simulationOutput <- simulateResiduals(fittedModel = model_submit1, plot = F)
```

https://stats.stackexchange.com/questions/531601/dharma-quantile-deviations-detected
```{r}
plot(simulationOutput)
testQuantiles(simulationOutput, currNumCities_df$currNumCities)
testDispersion(simulationOutput)
```

## remaining budget at the end of trial 

```{r}
model_submit2 = lme4::glmer(submit ~  1 + sqrt(leftover) + (1 |subjects),
                                  data = currNumCities_df, family = "binomial")
summary(model_submit2)
simulationOutput <- simulateResiduals(fittedModel = model_submit2, plot = F)

```

```{r}
plot(simulationOutput)
testQuantiles(simulationOutput, sqrt(currNumCities_df$leftover))
testDispersion(simulationOutput)

```

## both
```{r}
model_submit3 = lme4::glmer(submit ~  1 + currNumCities + sqrt(leftover) + (1 |subjects),
                                  data = currNumCities_df, family = "binomial")
summary(model_submit3)
simulationOutput <- simulateResiduals(fittedModel = model_submit3, plot = F)

```
```{r}
plot(simulationOutput)
testDispersion(simulationOutput)

```

```{r}
anova(model_submit1, model_submit3, test="Chisq")
anova(model_submit2, model_submit3, test="Chisq")
```

## puzzle MAS
```{r}
single_condition_data = data_puzzle_level[(data_puzzle_level['condition']==1), c("mas", "subjects", "numFullUndo")]
```

```{r}
model_undo_brms = glmmTMB(numFullUndo ~  1  + mas ,
                                  data = single_condition_data,  
                                  ziformula=~1,
                                  family = "nbinom1")
```

```{r}
summary(model_undo_brms)
simulationOutput <- simulateResiduals(fittedModel = model_undo_brms, plot = F)

```
```{r}
plot(simulationOutput)

```
# when errors
## step

```{r}
idx = (data_choice_level['condition']==0)&(data_choice_level['within_reach']!=0)
data_subset = data_choice_level[idx, ]
data_subset["step"] = data_subset$currNumCities / data_subset$allMAS
```

```{r}
model_undo = lme4::glmer(error ~  1 + step + (1|subjects),
                                  data = data_subset, family = "binomial")

# get the coefficients for the best fitting model
summary(model_undo)
simulationOutput <- simulateResiduals(fittedModel = model_undo, plot = F)
```

```{r}
plot(simulationOutput)

```

# made errors
## sum of severity of error until last step

```{r}
idx = (data_choice_level['condition']==1)&(data_choice_level['currNumCities']!=1)&(data_choice_level['submit']!=1)
index_error =  as.numeric(rownames(data_choice_level[idx,]))
total_error = data_choice_level[index_error,'allMAS'] - data_choice_level[index_error,'currMas']

df_error_undo = data_choice_level[index_error+1, c('subjects','puzzleID', "firstUndo")]
df_error_undo["accumulatedError"] = total_error
```

```{r}
model_error_undo = lme4::glmer(firstUndo ~  1 + log(accumulatedError+1) + (1|subjects),
                                  data = df_error_undo, family = "binomial")
summary(model_error_undo)
simulationOutput <- simulateResiduals(fittedModel = model_error_undo, plot = F)
```
```{r}
plot(simulationOutput)
```

