---
title: "final_statistics"
author: "sherry"
date: "2023-06-19"
output: html_document
---
# setup
## load
```{r}
rm(list=ls())

knitr::opts_chunk$set(echo = FALSE)

library(lme4)
library(lmerTest)
library(DHARMa)
library(rcompanion)
#library(glmmTMB)
#library(cAIC4)
# library(BayesFactor)

pathToFolder <- "/Users/dbao/My_Drive/road_construction/data/2022_online/"
save_folder <- file.path(pathToFolder, 'stat_model/final/')
data_folder <- file.path(pathToFolder, 'R_analysis_data/')

undo_data <- read.csv(file.path(data_folder, "statsdata_undo_data.csv"))

RT_nonterminal <- read.csv(file.path(data_folder, "statsdata_rt_nonterminal.csv"))
RT_terminal <- read.csv(file.path(data_folder, "statsdata_rt_terminal.csv"))

error_data <- read.csv(file.path(data_folder, "error_data_undo_condition.csv"))

```

# Error
## Move Error Magnitude
```{r}
model_error = glm(severityOfErrors ~  1  + budget_change + within_reach_change,
                                  data = error_data[error_data$checkEnd==0,], family = "poisson")
summary(model_error)

simulationOutput <- simulateResiduals(fittedModel = model_error, n = 1000, plot = F)
plot(simulationOutput)
```

## Cumulative error
```{r}
model_error_terminal = glm(cumulative_error ~  1 + currNumCities + leftover + budget_change + within_reach_change,
                                  data = error_data[error_data$checkEnd==1,], family = poisson)
summary(model_error_terminal)
simulationOutput <- simulateResiduals(fittedModel = model_error_terminal, n = 1000, plot = F)
plot(simulationOutput)
```

# Undo - error
## Number of connected cities
```{r}
load(file.path(save_folder, 'model_undo_step.RData'))
load(file.path(save_folder, 'model2_undo_step.RData'))
compareGLM(model_undo, model_undo2)
```
```{r}
load(file.path(save_folder, 'model_undo_step.RData'))
simulationOutput <- simulateResiduals(fittedModel = model_undo, n = 1000, plot = F)
plot(simulationOutput)
```
## Sequential - error magnitude
### Probability
```{r}
load(file.path(save_folder, 'model_undo_error_magnitude.RData'))
simulationOutput <- simulateResiduals(fittedModel = model_undo, n = 1000, plot = F)
plot(simulationOutput)
```
```{r}
load(file.path(save_folder, 'model_sequential_undo_error_magnitude.RData'))
simulationOutput <- simulateResiduals(fittedModel = model_undo, n = 1000, plot = F)
plot(simulationOutput)
```
```{r}
load(file.path(save_folder, 'model_single_undo_error_magnitude.RData'))
simulationOutput <- simulateResiduals(fittedModel = model_undo, n = 1000, plot = F)
plot(simulationOutput)
```

### Proportion
```{r}
load(file.path(save_folder, 'model_prop_single_undo_error_magnitude.RData'))
simulationOutput <- simulateResiduals(fittedModel = model_undo, n = 1000, plot = F, re.form = NULL) # 
plot(simulationOutput)

testUniformity(simulationOutput) 
testQuantiles(simulationOutput)
```

# Undo - State and move features
## non-terminal
The standardized coefficients represent the change in the outcome variable for a one standard deviation change in the predictor variable, which might alter how interactions are interpreted and their significance in the model.
```{r}
data_df = undo_data[(undo_data$N_more>0),]
print(cor.test(data_df$currNumCities, data_df$leftover_new))

model_undo_nonterminal0 = glm(firstUndo ~  1 + leftover*N_more + currNumCities*N_more + budget_change + within_reach_change,
data = data_df, family = binomial(link="logit"))
summary(model_undo_nonterminal0)

# model_undo_nonterminal1 = glm(firstUndo ~  1 + leftover_new*N_more + budget_change_new*N_more + within_reach_change_new*N_more,
# data = data_df, family = binomial(link="logit"))
# 
# model_undo_nonterminal2 = glm(firstUndo ~  1 + currNumCities_new*N_more + budget_change_new*N_more + within_reach_change_new*N_more,
# data = data_df, family = binomial(link="logit"))

```

```{r}
compareGLM(model_undo_nonterminal0, model_undo_nonterminal1,model_undo_nonterminal2)
```

```{r}
simulationOutput <- simulateResiduals(fittedModel = model_undo_nonterminal2, n = 1000, plot = F, re.form = NULL) # 
plot(simulationOutput)
```
## terminal
```{r}
data_df <- undo_data[(undo_data$N_more == 0),]
model_undo_terminal1 = glm(firstUndo ~  1 + currNumCities + leftover + budget_change+ within_reach_change ,
                                  data = data_df, family = binomial(link="logit"))
summary(model_undo_terminal1)
```

```{r}
print(cor.test(data_df$currNumCities_new,data_df$leftover_new))
print(cor.test(data_df$within_reach_change_new,data_df$budget_change_new))
print(cor.test(data_df$leftover_new,data_df$budget_change_new))

compareGLM(model_undo_terminal1,model_undo_terminal2,
           model_undo_terminal3,model_undo_terminal4)
summary(model_undo_terminal1)

BF_BIC_terminal = exp((BIC(model_undo_terminal4) - BIC(model_undo_terminal3))/2)
print(BF_BIC_terminal)
```

```{r}
simulationOutput <- simulateResiduals(fittedModel = model_undo_terminal3, n = 1000, plot = F, re.form = NULL) # 
plot(simulationOutput)
```


# Uncertainty
#### First-move RT
```{r}
load(file.path(save_folder, 'model_undo_rt1.RData'))
simulationOutput <- simulateResiduals(fittedModel = model_undo, n = 1000, plot = F) #, re.form = NULL
plot(simulationOutput)

testZeroInflation(simulationOutput)
testQuantiles(simulationOutput)
```


# RT
```{r}
model_RT <- lmerTest::lmer(RT_log ~  1 + currNumCities + undo + (1 |subjects) + (1|puzzleID),
                                  data = RT_nonterminal[RT_nonterminal$currNumCities>=1,])
simulationOutput <- simulateResiduals(fittedModel = model_RT, n = 1000, plot = F) #, re.form = NULL
plot(simulationOutput)
summary(model_RT)
```

```{r}
model_RT <- lmerTest::lmer(
  RT_log ~  1 + currNumCities + firstUndo + (1|subjects) + (1|puzzleID),
                        data = RT_terminal)
simulationOutput <- simulateResiduals(fittedModel = model_RT, n = 1000, plot = F) #, re.form = NULL
plot(simulationOutput)
summary(model_RT)
```

# Undo Completion
## what predicts the undo terminal
```{r}
load(file.path(save_folder, 'model_undo_right_error_and_cumulative.RData'))
simulationOutput <- simulateResiduals(fittedModel = model_undo_right, n = 2000, plot = F) #, re.form = NULL
plot(simulationOutput)

testZeroInflation(simulationOutput)
testQuantiles(simulationOutput)
```

