---
title: "final_statistics"
author: "sherry"
date: "2023-06-19"
output: html_document
---
# setup
```{r}
rm(list=ls())

knitr::opts_chunk$set(echo = FALSE)

library(lme4)
library(lmerTest)
# library(DHARMa)
# library(rcompanion)
library(dplyr)
library(marginaleffects)
#library(glmmTMB)
#library(cAIC4)
# library(BayesFactor)

pathToFolder <- "/Users/dbao/Library/CloudStorage/GoogleDrive-sherrydbao@gmail.com/My Drive/road_construction_data/data/2022_online/"
save_folder <- file.path(pathToFolder, 'stat_model/final/')
data_folder <- file.path(pathToFolder, 'R_analysis_data')

undo_data <- read.csv(file.path(data_folder, "statsdata_undo_data.csv"))
undo_data["RT1_log"] = log(undo_data["RT1"]+1)

state_df_1undo <- read.csv(file.path(data_folder, "state_df_1undo.csv"))

error_data <- read.csv(file.path(data_folder, "error_data_undo_condition.csv"))
error_data["RT1_log"] = log(error_data["RT1"]+1)

```

# Undo - prospective
```{r}
state_df_1undo$subjects <- as.factor(state_df_1undo[,"subjects"])
state_df_1undo$puzzleID <- as.factor(state_df_1undo[,"puzzleID"])
state_df_1undo$error <- as.factor(state_df_1undo[,"error"])
state_df_1undo$action_gap_z <- scale(state_df_1undo[,"action_gap"])
state_df_1undo$cumulative_error_z <- scale(state_df_1undo[,"cumulative_error"])
state_df_1undo$RT1_log_z <- scale(state_df_1undo[,"RT1_log"])
state_df_1undo$RT1_z <- scale(state_df_1undo[,"RT1"])

model_undo = lme4::glmer(firstUndo ~  1 + action_gap_z*cumulative_error_z + (1 |subjects)+(1|puzzleID),
data = state_df_1undo, family = binomial(link="logit"))

summary(model_undo)

# only cumulative_error_z in puzzleID as we don't believe the relationship between action_gap_z and firstUndo would differ that much
model_undo_full = lme4::glmer(firstUndo ~  1 + action_gap_z*cumulative_error_z + (1+ action_gap_z|subjects)+(1+ cumulative_error_z |puzzleID),
data = state_df_1undo, family = binomial(link="logit"),
  control = lme4::glmerControl(
    optimizer = "bobyqa",
    optCtrl = list(maxfun = 2e5)
  ))

summary(model_undo_full)

model_undo_noag = lme4::glmer(firstUndo ~  1 + cumulative_error_z + (1|subjects)+(1+ cumulative_error_z |puzzleID),
data = state_df_1undo, family = binomial(link="logit"),
  control = lme4::glmerControl(
    optimizer = "bobyqa",
    optCtrl = list(maxfun = 2e5)
  ))
summary(model_undo_noag)

mc = anova(model_undo_noag, model_undo_full, test = "Chisq")

# af <- lme4::allFit(model_undo_full)
# summary(af)


model_undo2 = lme4::glmer(firstUndo ~  1 + RT1_log_z * cumulative_error_z + (1 |subjects)+(1|puzzleID),
                                  data = state_df_1undo, family = binomial(link="logit"))

summary(model_undo2)

model_undo2_full = lme4::glmer(firstUndo ~  1 + RT1_log_z * cumulative_error_z + (1+RT1_log_z|subjects)+( 1+cumulative_error_z|puzzleID),
                                  data = state_df_1undo, family = binomial(link="logit"),
                               control = lme4::glmerControl(
    optimizer = "bobyqa",
    optCtrl = list(maxfun = 2e5)
  ))

summary(model_undo2_full)

mc2 = anova(model_undo_noag, model_undo2_full, test = "Chisq")

# avg_slopes(
#   model_undo2_full,
#   variables = "RT1_log_z",
#   type = "link"       # average d(log-odds)/dRT
# )

# error_rt1 = lmerTest::lmer(cumulative_error ~  1 + RT1_log + (1 |subjects)+(1|puzzleID),
#                                   data = state_df_1undo)
# summary(error_rt1)
# 
# error_gap = lmerTest::lmer(cumulative_error ~  1 + action_gap + (1 |subjects)+(1|puzzleID),
#                                   data = state_df_1undo)
# summary(error_gap)
# 
# rt1_gap = lmerTest::lmer(RT1_log ~  1 + action_gap + (1 |subjects)+(1|puzzleID),
#                                   data = state_df_1undo)
# summary(rt1_gap)
```

```{r}
result1 = slopes(model_undo, variables = "action_gap", by = "error", type = "link")

result2 = slopes(model_undo2, variables = "RT1_log", by = "error", type = "link")
```

```{r}
# load(file.path(save_folder, 'model_undo_rt1.RData'))
# simulationOutput <- simulateResiduals(fittedModel = model_undo, n = 1000, plot = F) #, re.form = NULL
# plot(simulationOutput)
# 
# testZeroInflation(simulationOutput)
# testQuantiles(simulationOutput)
```


# Undo - cumulative error * terminal
```{r}
# model_undo = lme4::glmer(firstUndo ~  1 + cumulative_error*checkEnd  + (1 |subjects) + (1|puzzleID),
#                                   data = undo_data, family = "binomial")
undo_data$cumulative_error_z <- scale(undo_data[,"cumulative_error"])

model_undo_full = lme4::glmer(firstUndo ~  1 + cumulative_error_z*checkEnd  + (1 + cumulative_error_z + checkEnd |subjects) + (1 + cumulative_error_z + checkEnd|puzzleID),
                                  data = undo_data, family = "binomial",
                              control = glmerControl(optimizer = "bobyqa",
                                      optCtrl = list(maxfun = 1e5)))
# summary(model_undo)
summary(model_undo_full)
```
```{r}
result1 = slopes(model_undo_full, variables = "cumulative_error_z", by = "checkEnd", type = "link")
result1
```


# Undo - state and move features
### non-terminal
The standardized coefficients represent the change in the outcome variable for a one standard deviation change in the predictor variable, which might alter how interactions are interpreted and their significance in the model.
```{r}
data_df = undo_data[(undo_data$N_more>0),]
# print(cor.test(data_df$currNumCities, data_df$leftover_new))

model_undo_nonterminal0 = glm(firstUndo ~  1 + RT1_log + leftover*N_more + currNumCities*N_more + budget_change + within_reach_change,
data = data_df, family = binomial(link="logit"))
summary(model_undo_nonterminal0)

# model_undo_nonterminal0 = lme4::glmer(firstUndo ~  1 + leftover_new*N_more + currNumCities*N_more + budget_change_new + within_reach_change_new + (1 |subjects) + (1|puzzleID),
# data = data_df, family = binomial(link="logit"))
# summary(model_undo_nonterminal0)

# model_undo_nonterminal1 = glm(firstUndo ~  1 + leftover_new*N_more + budget_change_new*N_more + within_reach_change_new*N_more,
# data = data_df, family = binomial(link="logit"))
# 
# model_undo_nonterminal2 = glm(firstUndo ~  1 + currNumCities_new*N_more + budget_change_new*N_more + within_reach_change_new*N_more,
# data = data_df, family = binomial(link="logit"))

```

```{r}
compareGLM(model_undo_nonterminal0, model_undo_nonterminal1,model_undo_nonterminal2)
```

```{r}
simulationOutput <- simulateResiduals(fittedModel = model_undo_nonterminal0, n = 1000, plot = F, re.form = NULL) # 
plot(simulationOutput)
```

### terminal
```{r}
data_df <- undo_data[(undo_data$N_more == 0),]
model_undo_terminal1 = glm(firstUndo ~  1 + RT1_log + currNumCities + leftover + budget_change+ within_reach_change ,
                                  data = data_df, family = binomial(link="logit"))
summary(model_undo_terminal1)
```

```{r}
print(cor.test(data_df$currNumCities_new,data_df$leftover_new))
print(cor.test(data_df$within_reach_change_new,data_df$budget_change_new))
print(cor.test(data_df$leftover_new,data_df$budget_change_new))

compareGLM(model_undo_terminal1,model_undo_terminal2,
           model_undo_terminal3,model_undo_terminal4)
summary(model_undo_terminal1)

BF_BIC_terminal = exp((BIC(model_undo_terminal4) - BIC(model_undo_terminal3))/2)
print(BF_BIC_terminal)
```

```{r}
simulationOutput <- simulateResiduals(fittedModel = model_undo_terminal3, n = 1000, plot = F, re.form = NULL) # 
plot(simulationOutput)
```

# RT - cumulative error * terminal
```{r}
RT_all <- read.csv(file.path(data_folder, "statsdata_rt.csv"))
RT_all <- RT_all %>% 
  filter(abs(scale(RT))[] <= 3)
RT_all$cumulative_error_z <- scale(RT_all[,"cumulative_error"])
```

```{r}
# eq:stats_undoRT_error
model_RT <- lmerTest::lmer(RT_log ~  1 + cumulative_error_z * checkEnd  + (1 + cumulative_error_z  | subjects) + (1 |puzzleID),
                                  data = RT_all[(RT_all$undo==1),],         control = lmerControl(optimizer = "bobyqa",
                                      optCtrl = list(maxfun = 1e5)))

# simulationOutput <- simulateResiduals(fittedModel = model_RT, n = 1000, plot = F) #, re.form = NULL
# plot(simulationOutput)
summary(model_RT)
```
```{r}
result1 = slopes(model_RT, variables = "cumulative_error_z", by = "checkEnd")
```

# moveRT
```{r}
test_df <- read.csv(file.path(data_folder, "moveRT_df.csv"))

test_df$first_move = as.factor(test_df$first_move)
test_df$first_move = relevel(test_df$first_move, ref="False") 
test_df$condition = as.factor(test_df$condition)
test_df$subjects = as.factor(test_df$subjects)
test_df$puzzleID = as.factor(test_df$puzzleID)
```

```{r}
model_rt_full = lmerTest::lmer(log_RT ~  1 + first_move+condition  + (1+first_move|subjects) + (1+first_move|puzzleID),  
                data = test_df,
                control = lmerControl(optimizer = "bobyqa",
                                      optCtrl = list(maxfun = 1e5)))
print(summary(model_rt_full))  
```


